\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-15 paper/ms.tex
New figure, moved command line options to an appendix
appendices, mention DNEST4_PATH

@@

@@

Additional options are available on the command line. These are:\\

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.\\

@@

>>>>

We recommend you create an environment variable called \code{DNEST4\_PATH}
and set it to the directory {\em above} the \pkg{DNest4} directory. Then,
if the examples or templates from the \pkg{DNest4} repository are copied
to any other location on your system, their Makefiles will continue to work.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/regression_lines.pdf}
\caption{Regression lines drawn from the posterior.
\label{fig:regression_lines}}
\end{figure}

@@

Additional options are available on the command line. These are
described in Appendix~\ref{sec:command_line_options}.

@@

\appendix
\section{Command Line Options}\label{sec:command_line_options}
The following command line options are available.\\

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.
In our experience, \code{-c 10} tends to work better than the default
The output units remain in nats.
This option is incompatible with setting the maximum number of levels to 0
(automatic) in the OPTIONS file.
\\

\section{Specifying models in Python with dnest4.builder}

\section{Specifying models in Julia}
